Learning Libraries of Subroutines for Neurally--Guided Bayesian Program Learning

### 2018-05-15 nips_2018.tex
reverse example

We apply \system to three domains:
 symbolic regression; FlashFill-style~\cite{gulwani2011automating} string processing; and Lisp-style functions on lists.
 For each of these we initially provide a generic
 set of programming primitives in a Lisp-like language.
% including conditionals, variables, and higher-order functions.
 Our algorithm then discovers
 its own domain-specific vocabulary for expressing solutions in the domain (Tbl.~\ref{initialExampleDSL}).
\begin{wrapfigure}{r}{0.6\textwidth}
    \begin{tabular}{ll}
   \toprule
   Domain&Part of the learned DSL\\\midrule
   %% Circuits&\code{(nand (nand a a) (nand b b))}\\
   %% &\hspace{0.5cm} \emph{(an OR gate)}\\
   Regression& \code{(+ (* real x) real)} \\
      &\hspace{0.5cm} \emph{(a linear function of x)}\\
   Strings& \code{(map (lambda (x) (if (= x a) b x)))}\\
   &\hspace{0.5cm} \emph{(replace occurrences of a w/ b)}\\
   Lists& \code{(map (lambda (x) (+ x k)) l)}\\
   &\hspace{0.5cm} \emph{(add k to every element of list l)}
   \\\bottomrule
    \end{tabular}
    \caption{ Examples of structure found in DSLs  learned by our algorithm. \system builds a new DSL by discovering and reusing useful subroutines.}\label{initialExampleDSL}\vspace{-1cm}
 \end{wrapfigure}

>>>>

We apply \system to three domains:
 symbolic regression; FlashFill-style~\cite{gulwani2011automating} string processing; and Lisp-style functions on lists.
 For each of these we initially provide a generic
 set of programming primitives in a Lisp-like language.
% including conditionals, variables, and higher-order functions.
 Our algorithm then discovers
 its own domain-specific vocabulary for expressing solutions in the domain (Tbl.~\ref{initialExampleDSL}).
\begin{wrapfigure}{r}{0.6\textwidth}
    \begin{tabular}{ll}
   \toprule
   Domain&Part of the learned DSL\\\midrule
   %% Circuits&\code{(nand (nand a a) (nand b b))}\\
   %% &\hspace{0.5cm} \emph{(an OR gate)}\\
   Regression& \code{(+ (* real x) real)} \\
      &\hspace{0.5cm} \emph{(a linear function of x)}\\
   Strings& \code{(map (lambda (x) (if (= x a) b x)))}\\
   &\hspace{0.5cm} \emph{(replace occurrences of a w/ b)}\\
   Lists& \code{(fold nil (lambda (a b) (cons a b)))}\\
   &\hspace{0.5cm} \emph{(reverses a list)}
   \\\bottomrule
    \end{tabular}
    \caption{ Examples of structure found in DSLs  learned by our algorithm. \system builds a new DSL by discovering and reusing useful subroutines.}\label{initialExampleDSL}\vspace{-1cm}
 \end{wrapfigure}
